---
title: "Search files in several OS"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval = FALSE}
library(locatefile)
```

## MS-DOS

### Find drive letters

`wmic logicaldisk get name`

`fsutil fsinfo drives` 

### DIR command help

`DIR /?`

### Find a file

Find all power point files in a drive letter

`DIR "*.pptx" /S`

Find all files that contain test*.txt and show
Modification time (W) and order by size /O:D (old files first)

`DIR "test*.txt" /S /T:W /O:D`

Old files last

`DIR "test*.txt" /S /T:W /O:-D`

Creation time is C and access time A.

### Find file of a given month

`DIR "test*.txt" /S /T:W /O:D | FINDSTR 10/2022`

### Find file with word in name

`DIR "test*.txt" /S /T:W /O:D | FINDSTR name`

With no case-sensitivity

`DIR "test*.txt" /S /T:W /O:D | FINDSTR /I name`

To change the format and report only the file path

`DIR "test*.txt" /S /T:W /O:-D /B | FINDSTR /I name`

## LINUX

### Find drive letters

In WSL

`ls -l /mnt`

### Find a file

Find all power point files in a drive letter

`cd /mnt/g; find . -name "*.pptx"`

list long format

`cd /mnt/g; find . -name "*.pptx" -ls`

find all R files changes in the last 4 months

`find . -name "*.R" ! -ctime +120`

Find all R files accessed in the last 4 month but more than 3 months ago and
list all files in the long format

`find . -name "*.R" ! -atime +120 -atime +90 -exec ls -l {} +`

## R

### Find drive letters

`LETTERS[fs::dir_exists(paste0(LETTERS, ":" ))]`

In WSL

`LETTERS[fs::dir_exists(paste0("/mnt/", letters))]`

### Find a file

Find all power point files in a drive letter

`fs::dir_info("G:/La meva unitat/R/", recurse = TRUE, glob = "*.Rmd", fail = FALSE)`

find all R files changes in the last 4 months

```
fs::dir_info("G:/La meva unitat/R/", recurse = TRUE, glob = "*.Rmd", fail = FALSE) |> 
  dplyr::filter( modification_time > lubridate::today() - 120) |> 
  dplyr::mutate(path = fs::path_dir(path), file = fs::path_file(path)) |> 
  dplyr::select(path, file, size, modification_time)
```


